---
title: "unit test practice"
format: html
editor: visual
---

## unit testing with the 'testthat' package

first install necessary packages

```{r}
#install.packages("testthat") #you need to comment out any install packages lines because they will run again every time you render
#install.packages("devtools")
#install.packages("remotes")

library(testthat)
library(devtools)
library(remotes)
```

write a function to practice the unit test
this function is going to find the mean value of each column and then return the lowest and highest mean value calculated ( in that order)

we would expect:
- numeric
- output should be a vector of length 2 
- the first vlaue should be smaller than the second value
```{r}

mean_range <- function(df){
  col_means <- apply(X = df, MARGIN = 2, FUN = mean, na.rm = TRUE) #return mean values of each column in a dataframe
  #find min and max values
  col_mean_max <- max(col_means)
  col_mean_min <- min(col_means)
  # return those values combined in min, max order
  return(c(col_mean_min, col_mean_max))
}

mean_range(df = mtcars)
```

Write unit tests
```{r}
expect_length(mean_range(df=mtcars), 2) # works if it doesn't return anything

expect_type(mean_range(df), is.numeric)
```

